Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-02 main.tex
:pencil: ML vs capacity-achieving decision threshold

		\begin{subsection}{Backscatter Detection}
			To reveal the impact of backscatter modulation on the primary transmission, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.

@@

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks. Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal. The corresponding decision rule is
			\begin{equation}
				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
				\label{eq:detection_threshold}
			\end{equation}

			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
				\label{eq:decision_region}
			\end{equation}
			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$. Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and thus follows Erlang distribution with shape $N$ and scale $\sigma_i^2$
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

			On top of \eqref{eq:decision_region} and \eqref{eq:energy_distribution}, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			Based on the equivalent point-to-point channel \eqref{eq:point_to_point_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-rate}
			Before investigating the sum-rate of the tags, we introduce some prerequisites in information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the information function associated with specific tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
				\label{eq:information_function}
			\end{equation}
			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ can be written as
			\begin{equation}
				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
				\label{eq:marginal_information_function}
			\end{equation}
			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{equation}
				I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
				\label{eq:mutual_information}
			\end{equation}

@@

		\begin{subsection}{Primary ergodic rate}
			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}. From the perspective of primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. As such, the ergodic primary rate can be expressed as
			\begin{align}
				R_s
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
				\label{eq:primary_ergodic_rate}
			\end{align}
			which is also a function of the tag input distribution $P(c_{\mathcal{K}})$.
		\end{subsection}
	\end{section}

	\begin{section}{Tag Input and Precoder Design}
		\begin{subsection}{Primary ergodic-secondary sum rate region}
			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision regions, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
			\begin{maxi!}
				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{\rho R_s + (1 - \rho) R_c}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
			\end{maxi!}
			where $\rho \in [0,1]$ denotes the priority of the primary link. As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{w}$ and $P(c_{\mathcal{K}})$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
		\end{subsection}

@@

		\begin{subsection}{Decision region}
			As indicated by \cite{Qian2019b}, the optimal ML decision regions are very close to the optimal decision regions to problem \eqref{op:weighted_sum_rate}. We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:mutual_information} w.r.t. $T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
		\end{subsection}

@@

	\begin{section}{The Single-tag Case}
		% \begin{figure}[!t]
		% 	\centering
		% 	\def\svgwidth{0.9\columnwidth}
		% 	\import{assets/}{symbiotic_radio.pdf_tex}
		% 	\caption{A single-user single-tag symbiotic radio system.}
		% 	\label{fi:symbiotic_radio}
		% \end{figure}
		As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems. In the primary AP-UE downlink system, the AP transmits to the single-antenna user. In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient. Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$. We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging. One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019g}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}. Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP. Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$. At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
		\begin{equation}
			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
		\end{equation}
		where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise. We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.

		\begin{remark}
			The symbiotic radio network can be regarded as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user. It is known that Superposition Coding-Successive Interference Cancellation (SC-SIC) with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}. Therefore, most relevant papers proposed the user to first decode the primary message (by treating the tag interference as noise), cancel out its contribution from the received signal, then decode the secondary message. Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding is expected to enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding is ideally interference-free.
		\end{remark}

		\begin{remark}
			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link. This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC. In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner. Therefore, for a fixed fading block, the primary transmission is able to achieve the ergodic capacity with artificial channel variation created by the backscatter modulation. [Channel over channel, randomness over randomness]
		\end{remark}

		\begin{subsection}{Backscatter Transmission}
			To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$. In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where

>>>>

		\begin{subsection}{Backscatter Detection}
			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.

@@

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} We also define $z \triangleq \lVert \boldsymbol{y} \rVert^2$ as the received signal energy over $N$ primary blocks, and $f(z \mid \mathcal{H}_i)$ as the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and thus follows Erlang distribution with shape $N$ and scale $\sigma_i^2$
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

			\begin{remark}
				The backscatter links essentially create a discrete-input continuous-output memoryless channel. To further reduce decoding complexity, we apply hard-decision detection and formulate a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds.
			\end{remark}

			For example, consider the Maximum-Likelihood (ML) detector where the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,j}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			and the corresponding decision rule is
			\begin{equation}
				\Lambda_{i,j}^{\mathrm{ML}}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j}^{\mathrm{ML}},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				T_{i,j}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
				\label{eq:detection_threshold}
			\end{equation}
			and we manually define $T_{0,1}^{\mathrm{ML}} \triangleq 0$ and $T_{M^K,M^K+1}^{\mathrm{ML}} \triangleq \infty$. Let $\mathcal{T}^{\mathrm{ML}} \triangleq \{T_{0,1}^{\mathrm{ML}},\ldots,T_{M^K,M^K+1}^{\mathrm{ML}}\}$.

			\begin{remark}
				Although the ML decision threshold set $\mathcal{T}^{\mathrm{ML}}$ is optimal in terms of the likelihood function, it is not necessarily the same with the capacity-achieving threshold set $\mathcal{T}^{\star}$. Interestingly, it was shown in \cite{Qian2019b} that $\mathcal{T}^{\mathrm{ML}}$ and $\mathcal{T}^{\star}$ are very close in the single-tag BIBO case.
			\end{remark}

			For any given threshold set $\mathcal{T} \triangleq \{T_{0,1},\ldots,T_{M^K,M^K+1}\}$, the decision region of hypothesis $\mathcal{H}_i$ is
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
				\label{eq:decision_region}
			\end{equation}
			which can be combined with \eqref{eq:energy_distribution} to formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix. The probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			Based on the equivalent point-to-point channel \eqref{eq:point_to_point_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. Hence, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, for every tag input combination with fixed threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-rate}
			Before investigating the sum-rate of the tags, we introduce some prerequisites in information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the information function associated with specific tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
				\label{eq:information_function}
			\end{equation}
			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is written as
			\begin{equation}
				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
				\label{eq:marginal_information_function}
			\end{equation}
			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{equation}
				I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
				\label{eq:mutual_information}
			\end{equation}

@@

		\begin{subsection}{Primary ergodic rate}
			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}. For primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. As such, the ergodic primary rate can be expressed as
			\begin{align}
				R_s
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
				\label{eq:primary_ergodic_rate}
			\end{align}
			which is also a function of the tag input distribution $P(c_{\mathcal{K}})$.
		\end{subsection}
	\end{section}

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary ergodic-secondary sum rate region}
			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision region, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
			\begin{maxi!}
				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{\rho R_s + (1 - \rho) R_c}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
			\end{maxi!}
			where $\rho \in [0,1]$ denotes the priority of the primary link. As problem \eqref{op:rate_region} is not jointly convex over $P(c_{\mathcal{K}})$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
		\end{subsection}

@@

		\begin{subsection}{Decision region}
			As indicated by \cite{Qian2019b}, the optimal ML decision regions are very close to the optimal decision regions to problem \eqref{op:rate_region}. We can either use \eqref{eq:decision_region} as suboptimal, or take derivative of \eqref{eq:mutual_information} w.r.t. $T_{i-1,i}$ and $T_{i,i+1}$ (however, closed-form solutions are unavailable and two-dimensional search is needed).
		\end{subsection}

@@

	% \begin{section}{The Single-tag Case}
	% 	% \begin{figure}[!t]
	% 	% 	\centering
	% 	% 	\def\svgwidth{0.9\columnwidth}
	% 	% 	\import{assets/}{symbiotic_radio.pdf_tex}
	% 	% 	\caption{A single-user single-tag symbiotic radio system.}
	% 	% 	\label{fi:symbiotic_radio}
	% 	% \end{figure}
	% 	As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems. In the primary AP-UE downlink system, the AP transmits to the single-antenna user. In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient. Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$. We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging. One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019g}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}. Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP. Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$. At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
	% 	\begin{equation}
	% 		y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
	% 	\end{equation}
	% 	where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise. We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.

	% 	\begin{remark}
	% 		The symbiotic radio network can be regarded as a special case of Multiple Access Channel (MAC) because the AP and the tag simultaneously transmit to the user. It is known that Superposition Coding-Successive Interference Cancellation (SC-SIC) with different decoding orders can achieve different vertices of the MAC capacity region \cite{Goldsmith2005}. Therefore, most relevant papers proposed the user to first decode the primary message (by treating the tag interference as noise), cancel out its contribution from the received signal, then decode the secondary message. Since the direct channel is typically much stronger than the cascaded channel \cite{Ozdogan2020}, the primary decoding is expected to enjoy a high Signal-to-Interference-and-Noise Ratio (SINR) and the secondary decoding is ideally interference-free.
	% 	\end{remark}

	% 	\begin{remark}
	% 		The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link. This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC. In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner. Therefore, for a fixed fading block, the primary transmission is able to achieve the ergodic capacity with artificial channel variation created by the backscatter modulation. [Channel over channel, randomness over randomness]
	% 	\end{remark}

	% 	\begin{subsection}{Backscatter Transmission}
	% 		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$. In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
	% 		\begin{equation}
